---
title: "causaldraw_intervention_2"
author: "Holly Huey"
date: "3/1/2021"
output: html_document
---

This script was written for the follow-up intervention_2 task of causaldraw_intervention. Previously, we analyzed RT and corrAns for locating *which element* to intervene on. 

This follow-up analyzing corrAns for *which intervention* to use to produce an effect. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(tidyr)
library(reshape2)
library(dplyr)
library(ggplot2)
library(stringr)
require(tidyboot)
library(emmeans)
library(ggeffects)
library(ggsignif)
```

## Load in data
```{r message = FALSE}
## note that this data has already been preprocessed so as to remove all identifiable information (originally collected on SONA)
final_data <- read_csv("../results/csv/causaldraw_intervention_2_processed_data.csv") 

#how many total participants?
length(unique(final_data$gameID))

## remove empty cols
final_data <- subset(final_data, select = -c(prolificID, sessionID, studyID, experiment_id, credit_token, key_check, corr_key))
```

## Split datasets
```{r}
practice <- final_data %>%
  filter(phase %in% c("practice")) %>% 
  droplevels()

processed_data <- final_data %>%
  filter(!(phase %in% c("practice"))) %>% 
  droplevels()
```

## Check for above chance in accuracy by condition
```{r}
## is explanatory above chance? 
final_data_exp <- final_data %>%
  filter(condition %in% c("explanatory"))

above_chance_exp <- glmer(corrAns ~ 1 + (1|orig_gameID), family='binomial', data=final_data_exp)
summary(above_chance_exp)

## is depictive above chance? 
final_data_dep <- final_data %>%
  filter(condition %in% c("depictive"))

above_chance_dep <- glmer(corrAns ~ 1 + (1|orig_gameID), family='binomial', data=final_data_dep)
summary(above_chance_dep)
```

## Analyses for corrAns
```{r}
## same analysis as in the original causaldraw_intervention
# m_corrAns <- glmer(corrAns ~ condition + condition*numCausal + condition*numFunctional + condition*numSymbol + condition*numBackground + (1|sketchID) + (1|orig_gameID), family="binomial", data=final_data, nAGQ=0)
# summary(m_corrAns)

m_corrAns <- glmer(corrAns ~ condition + numCausal + numFunctional + numBackground + (1|sketchID) + (1|orig_gameID), family="binomial", data=final_data, nAGQ=0)
summary(m_corrAns)
```

### plot for corrAns
```{r}
df_corrAns <- ggpredict(m_corrAns, terms = c("condition"))

## making plot
plot_corrAns <- ggplot(df_corrAns, aes(x, predicted, fill=x)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  xlab("condition") +
  ylab("corrAns") +
  scale_x_discrete(labels=c("depict", "explain")) +
  ylim(0,1) +
  theme_light() +
  theme(axis.text.x = element_text(size = 6), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

plot_corrAns + scale_fill_manual(values=c("#919191", "#00766e"))
```

### raw plot for corrAns
```{r}
## making plot
plot_corrAns <- final_data %>% 
  ggplot(aes(x=condition, y=corrAns, fill=condition)) +
  geom_bar(aes(y=corrAns), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  xlab("condition") +
  ylab("corrAns") +
  scale_x_discrete(labels=c("depict", "explain")) +
  ylim(0,1) +
  theme_light() +
  theme(axis.text.x = element_text(size = 6), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

plot_corrAns + scale_fill_manual(values=c("#919191", "#00766e"))
```

## Analyses for RT
```{r}
final_data_RT_corrAns <- final_data %>% 
  filter((corrAns %in% c(1))) %>% 
  droplevels()

m_rt <- lmer(log(rt) ~ condition + condition*numCausal + condition*numFunctional + condition*numSymbol + condition*numBackground + (1|sketchID) + (1|orig_gameID), data=final_data_RT_corrAns, REML=FALSE)
summary(m_rt) 
```

### plot for RT
```{r}
df_rt <- ggpredict(m_rt, terms = "condition")

## making plot
plot_rt <- ggplot(df_rt, aes(x, predicted, fill=x)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width = 0) +
  xlab("condition") +
  ylab("rt") +
  scale_x_discrete(labels=c("depict", "explain")) +
  ylim(0, 8000) +
  theme_light() +
  theme(axis.text.x = element_text(size = 6), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

plot_rt + scale_fill_manual(values=c("#919191", "#00766e"))
```

### raw plot for RT
```{r}
## making plot
plot_rt <- final_data_RT_corrAns %>%  
  ggplot(aes(x=condition, y=rt, fill=condition)) +
  geom_bar(aes(y=rt), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  xlab("condition") +
  ylab("rt") +
  scale_x_discrete(labels=c("depict", "explain")) +
  ylim(0, 8000) +
  theme_light() +
  theme(axis.text.x = element_text(size = 6), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

plot_rt + scale_fill_manual(values=c("#919191", "#00766e"))
```

