---
title: "causaldraw_identification"
author: "Holly Huey"
date: "9/21/2020"
output:
  html_document: default
---

This script was written for identification task to analyze how accurately and quickly participants could match a presented drawing (visual explanation or depiction) to the target referent.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(tidyr)
library(reshape2)
library(dplyr)
library(ggplot2)
library(stringr)
require(tidyboot)
library(emmeans)
library(ggeffects)
library(ggsignif)
```

## Load in data
```{r message = FALSE}
## note that this data has already been preprocessed so as to remove all identifiable information (originally collected on SONA)
final_data <- read_csv("../results/csv/causaldraw_identification_processed_data_random_sample.csv")
```

```{r}
# do we want to only analyze RTs for correct responses? 
final_data_RT <- final_data %>% 
  filter((corrAns %in% c(1))) %>% 
  droplevels()
```

##Analyses for RT
```{r}
#NOTE! Only using RTs of correct responses

## full model for RT
# m_fullRT <- lmer(log(final_data_RT$rt) ~ condition + condition*numCausal + condition*numFunctional + condition*numSymbol + condition*numBackground + (1|sketchID) + (1|toy_type) + (1|orig_gameID) + (totalStrokes|condition) + (totalStrokes|toy_type), data=final_data_RT, REML=FALSE)
# summary(m_fullRT)

## reduced model, since the previous was overfitted
m_reducedRT <- lmer(log(rt) ~ condition + condition*numCausal + condition*numFunctional + condition*numSymbol + condition*numBackground + (1|sketchID) + (1|orig_gameID), data=final_data_RT, REML=FALSE)
summary(m_reducedRT)
```

### assessing model fit w/o parameters
```{r}
simple_RT <- lmer(log(rt) ~ condition + (1|sketchID) + (1|orig_gameID), data=final_data_RT, REML=FALSE)
summary(simple_RT)
```

```{r}
RT_all_responses <- lmer(log(rt) ~ condition + (1|sketchID) + (1|orig_gameID), data=final_data, REML=FALSE)
summary(RT_all_responses)
```

### plot for RT
```{r}
## getting predictions
df_rt <- ggpredict(simple_RT, terms = "condition")

## making plot
plot_rt <- ggplot(df_rt, aes(x, predicted, fill=x)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width = 0) +
  geom_signif(annotation = "***",
          y_position = 2750,
          xmin = "depictive",
          xmax = "explanatory",
          tip_length = 0) +
  geom_text(aes(label = predicted), position=position_dodge(width=0.9), vjust=-0.25) +
  xlab("condition") +
  ylab("rt") +
  scale_x_discrete(labels=c("depict", "explain")) +
  ylim(0, 8000) +
  theme_light() +
  theme(axis.text.x = element_text(size = 6), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none")

plot_rt + scale_fill_manual(values=c("#919191", "#00766e"))

# ggsave('../results/plots/identification_rt.pdf', height = 8, width = 6,  units = 'cm', useDingbats = F)
# ggsave('../results/plots/identification_rt_simple.pdf', height = 8, width = 3.25,  units = 'cm', useDingbats = F)
```

##Analyses for corrAns
```{r}
## full model for corrAns
# m_fullcorrAns <- glmer(final_data$corrAns ~ condition + condition*numCausal + condition*numFunctional + condition*numSymbol + condition*numBackground + (1|sketchID) + (1|toy_type) + (1|orig_gameID) + (totalStrokes|condition) + (totalStrokes|toy_type), family="binomial", data=final_data, nAGQ=0)
# summary(m_fullcorrAns)

final_exp <- final_data %>% 
  filter(condition %in% c('explanatory'))
mean(final_exp$corrAns)

final_dep <- final_data %>% 
  filter(condition %in% c('depictive'))
mean(final_dep$corrAns)

## reduced model, since the previous was overfitted
#https://stats.stackexchange.com/questions/304132/glmer-not-converging
m_reducedcorrAns <- glmer(corrAns ~ condition + condition*numCausal + condition*numFunctional + condition*numSymbol + condition*numBackground + (1|sketchID) + (1|orig_gameID), family="binomial", data=final_data, nAGQ=0)
summary(m_reducedcorrAns)
```

## assessing model fit w/o predictors
```{r}
simple_m <- glmer(corrAns ~ condition + (1|sketchID) + (1|orig_gameID), family="binomial", data=final_data, nAGQ=0)
summary(simple_m)
```

```{r}
anova(simple_m, m_reducedcorrAns)
```

### plot for corrAns
```{r}
df_corrAns <- ggpredict(simple_m, terms = c("condition"))

## making plot
plot_corrAns <- ggplot(df_corrAns, aes(x, predicted, fill=x)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  geom_signif(annotation = "***",
          y_position = 0.95,
          xmin = "depictive",
          xmax = "explanatory",
          tip_length = 0) +
  geom_text(aes(label = predicted), position=position_dodge(width=0.9), vjust=-0.25) +
  xlab("condition") +
  ylab("corrAns") +
  scale_x_discrete(labels=c("depict", "explain")) +
  ylim(0,1) +
  geom_hline(yintercept=0.5, linetype='dashed', color='black', size=0.5) +
  theme_light() +
  theme(axis.text.x = element_text(size = 6), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none") 
  # geom_jitter(data = final_sketch, aes(x=condition, y=corrAns, fill=condition), alpha = 0.4, shape = 21, width=0.3) 

plot_corrAns + scale_fill_manual(values=c("#919191", "#00766e"))

# ggsave('../results/plots/identification_corrAns.pdf', height = 8, width = 6,  units = 'cm', useDingbats = F)
# ggsave('../results/plots/identification_corrAns_simple.pdf', height = 8, width = 3,  units = 'cm', useDingbats = F)
```

### check for above chance in accuracy 
```{r}
## is explanatory above chance? 
above_chance_exp <- glmer(corrAns ~ 1 + (1|orig_gameID), family='binomial', data=final_exp)
summary(above_chance_exp)
```

```{r}
## is depictive above chance? 
above_chance_dep <- glmer(corrAns ~ 1 + (1|orig_gameID), family='binomial', data=final_dep)
summary(above_chance_dep)
```

## follow-up exploratory analyses

```{r}
## first calculate mean corrAns for each sketchID, so that the scatterplots represent each sketch
final_sketch <- final_data %>% 
  select(sketchID, condition, corrAns, numBackground, numCausal, numFunctional, numSymbol, totalStrokes) %>% 
  group_by(sketchID, condition) %>% 
  summarise(across(everything(), mean)) %>% 
  mutate(numBCK = ifelse(numBackground <= median(.$numBackground), "low", "high")) %>% 
  mutate(numCSL = ifelse(numCausal <= median(.$numCausal), "low", "high")) %>% 
  mutate(numFNC = ifelse(numFunctional <= median(.$numFunctional), "low", "high")) %>% 
  mutate(numSYM = ifelse(numSymbol <= median(.$numSymbol), "low", "high")) %>% 
  mutate(numTOTAL = ifelse(totalStrokes <= median(.$totalStrokes), "low", "high"))

## recode data by median split
final_data <- final_data %>% 
  mutate(numBCK = ifelse(numBackground <= median(.$numBackground), 'low', 'high')) %>% 
  mutate(numCSL = ifelse(numCausal <= median(.$numCausal), 'low', 'high')) %>% 
  mutate(numFNC = ifelse(numFunctional <= median(.$numFunctional), 'low', 'high')) %>% 
  mutate(numSYM = ifelse(numSymbol <= median(.$numSymbol), 'low', 'high')) %>% 
  mutate(numTOTAL = ifelse(totalStrokes <= median(.$totalStrokes), 'low', 'high'))
```

### how does the number of STRUCTURAL details impact performance?
```{r}
final_sketch %>% 
  ggplot(aes(x=numBackground, y=corrAns)) +
  geom_point(aes(color = condition)) +
  geom_smooth(method=lm, aes(color = factor(condition))) +
  geom_smooth(method=lm) +
  theme_light() 
```

```{r}
## how does numBackground impact performance?
structural <- glmer(corrAns ~ numBackground + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(structural)
```

```{r}
## plot of raw data w/ median split
final_data %>% 
  ggplot(aes(x=numBCK, y=corrAns, fill=numBCK)) +
  geom_bar(stat="summary", width = .7, position = position_dodge(width = .75)) +
  facet_grid(.~condition) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numBackground') +
  theme_light() 
```

```{r}
## median split
background_strokes <- glmer(corrAns ~ numBCK + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(background_strokes)
```

```{r}
## is there an interaction between strokes + condition?
background_condition <- glmer(corrAns ~ condition*numBCK + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(background_condition)
```

```{r}
background_check <- glmer(corrAns ~ condition + numBCK + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
anova(background_check, background_condition)
```

```{r}
## is there a significant effect of including numBCK independently, than when interacting with condititon?
anova(background_strokes, background_condition)
```

```{r}
## plot estimated means w/ 95% CIs
background_m <- ggpredict(background_condition, terms = c("condition", "numBCK"))

ggplot(background_m, aes(group, predicted, fill=group)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  facet_grid(.~x) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numBackground') +
  theme_light() 
```

### how does the number of CAUSAL details impact performance?
```{r}
final_sketch %>% 
  ggplot(aes(x=numCausal, y=corrAns)) +
  geom_point(aes(color = condition)) +
  geom_smooth(method=lm, aes(color = factor(condition))) +
  geom_smooth(method=lm) +
  theme_light() 
```

```{r}
causal <- glmer(corrAns ~ numCausal + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(causal)
```

```{r}
final_data %>% 
  ggplot(aes(x=numCSL, y=corrAns, fill=numCSL)) +
  geom_bar(stat="summary", width = .7, position = position_dodge(width = .75)) +
  facet_grid(.~condition) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numCausal') +
  theme_light() 
```

```{r}
## median split
causal_strokes <- glmer(corrAns ~ numCSL + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(causal_strokes)
```

```{r}
## is there an interaction?
causal_condition <- glmer(corrAns ~ condition*numCSL + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(causal_condition)
```

```{r}
causal_check <- glmer(corrAns ~ condition + numCSL + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
anova(causal_check, causal_condition)
```

```{r}
## is there a significant effect of including numCSL independently, than when interacting with condititon?
anova(causal_strokes, causal_condition)
```

```{r}
## plot estimated means w/ 95% CIs
causal_m <- ggpredict(causal_condition, terms = c("condition", "numCSL"))

ggplot(causal_m, aes(group, predicted, fill=group)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  facet_grid(.~x) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numCausal') +
  theme_light() 
```

### how does the number of FUNCTIONAL details impact performance?
```{r}
final_sketch %>% 
  ggplot(aes(x=numFunctional, y=corrAns)) +
  geom_point(aes(color = condition)) +
  geom_smooth(method=lm, aes(color = factor(condition))) +
  geom_smooth(method=lm) +
  theme_light() 
```

```{r}
final_data %>% 
  ggplot(aes(x=numFNC, y=corrAns, fill=numFNC)) +
  geom_bar(stat="summary", width = .7, position = position_dodge(width = .75)) +
  facet_grid(.~condition) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numFunctional') +
  theme_light() 
```

```{r}
functional <- glmer(corrAns ~ numFunctional + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(functional)
```

```{r}
## median split
functional_strokes <- glmer(corrAns ~ numFNC + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(functional_strokes)
```

```{r}
## is there an interaction?
functional_condition <- glmer(corrAns ~ condition*numFNC + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(functional_condition)
```

```{r}
functional_check <- glmer(corrAns ~ condition + numFNC + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
anova(functional_check, functional_condition)
```

```{r}
## is there a significant effect of including numFNC independently, than when interacting with condititon?
anova(functional_strokes, functional_condition)
```

```{r}
## plot estimated means w/ 95% CIs
functional_m <- ggpredict(functional_condition, terms = c("condition", "numFNC"))

ggplot(functional_m, aes(group, predicted, fill=group)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  facet_grid(.~x) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numFunctional') +
  theme_light() 
```

### how does the number of SYMBOL details impact performance?
```{r}
final_sketch %>% 
  ggplot(aes(x=numSymbol, y=corrAns)) +
  geom_point(aes(color = condition)) +
  geom_smooth(method=lm, aes(color = factor(condition))) +
  geom_smooth(method=lm) +
  theme_light() 
```

```{r}
final_data %>% 
  ggplot(aes(x=numSYM, y=corrAns, fill=numSYM)) +
  geom_bar(stat="summary", width = .7, position = position_dodge(width = .75)) +
  facet_grid(.~condition) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numSymbols') +
  theme_light() 
```

```{r}
symbol <- glmer(corrAns ~ numSymbol + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(symbol)
```

```{r}
## median split
symbol_strokes <- glmer(corrAns ~ numSYM + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(symbol_strokes)
```

```{r}
## is there an interaction?
symbol_condition <- glmer(corrAns ~ condition*numSYM + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(symbol_condition)
```

```{r}
symbol_check <- glmer(corrAns ~ condition + numSYM + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
anova(symbol_check, symbol_condition)
```

```{r}
## is there a significant effect of including numSYM independently, than when interacting with condititon?
anova(symbol_strokes, symbol_condition)
```

```{r}
## plot estimated means w/ 95% CIs
symbol_m <- ggpredict(symbol_condition, terms = c("condition", "numSYM"))

ggplot(symbol_m, aes(group, predicted, fill=group)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  facet_grid(.~x) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numSymbol') +
  theme_light() 
```

### how does the number of OVERALL details impact performance?
```{r}
final_sketch %>% 
  ggplot(aes(x=totalStrokes, y=corrAns)) +
  geom_point(aes(color = condition)) +
  geom_smooth(method=lm, aes(color = factor(condition))) +
  geom_smooth(method=lm) +
  theme_light() 
```

```{r}
## median split
final_data %>% 
  ggplot(aes(x=numTOTAL, y=corrAns, fill=numTOTAL)) +
  geom_bar(stat="summary", width = .7, position = position_dodge(width = .75)) +
  facet_grid(.~condition) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numStrokes') + 
  theme_light() 
```

```{r}
overall_strokes <- glmer(corrAns ~ totalStrokes + (1|sketchID),  family="binomial", data=final_data, nAGQ=0)
summary(overall_strokes)
```

```{r}
## median split
total_strokes <- glmer(corrAns ~ numTOTAL + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(total_strokes)
```

```{r}
total_condition <- glmer(corrAns ~ condition*numTOTAL + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
summary(total_condition)
```

```{r}
total_check <- glmer(corrAns ~ condition + numTOTAL + (1|sketchID), family="binomial", data=final_data, nAGQ=0)
anova(total_check, total_condition)
```

```{r}
## is there a significant effect of including numTOTAL independently, than when interacting with condititon?
anova(total_strokes, total_condition)
```

```{r}
## plot estimated means w/ 95% CIs
total_m <- ggpredict(total_condition, terms = c("condition", "numTOTAL"))

ggplot(total_m, aes(group, predicted, fill=group)) +
  geom_bar(aes(y=predicted), stat="summary", width = .75, position = position_dodge(width = 0.5)) +
  facet_grid(.~x) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), alpha = .8, size = .75, width=0) +
  scale_fill_manual("legend", values = c("high" = "orange", "low" = "blue")) +
  ggtitle('numTotal') +
  theme_light() 
```
