---
title: "causaldraw_annotations analysis"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

This script was written to analyze the semantic annotations collected for *causaldraw* (visual production task)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message = FALSE}
library(tidyverse)
library(lme4)
library(lmerTest)
library(tidyr)
library(dplyr)
library(ggrepel)
# detach(package:dplyr)
# detach(package:plyr)
library(ggplot2)
library(stringr)
require(tidyboot)
require(wesanderson)
```

## Load in and preprocess data
```{r message = FALSE}
## preprocessed data compiled across batches
orig_data <- read_csv("../results/csv/causaldraw_annotation_final_stoke_analysis_random_sample.csv")
orig_data <- subset(orig_data, select = -c(X1))

## original survey data with batch run on mturk
orig_survey1 <- read_csv("../results/csv/causaldraw_annotations_processed_survey_data.csv")
## collected more annotations to resolve some majority vote issues on SONA
orig_survey2 <- read_csv("../results/csv/causaldraw_annotations_processed_patch2_survey_data.csv")
## collected 2 more annotations for missing annotations for levers_1 on Prolific
orig_survey3 <- read_csv("../results/csv/causaldraw_annotations_processed_patch3_survey_data.csv")

orig_survey <- mget(paste0('orig_survey', c('1', '2', '3'))) %>%
   dplyr::bind_rows()
```

```{r}
## change some col names to match prior analyses
orig_data$toy_id <- orig_data$stimuli
final_data <- orig_data
final_data <- final_data %>% 
  separate(toy_id, c("toy_type", "toy_variant"), "_", remove = FALSE)
```

#post-demographic analysis
```{r}
##count total participants
length(unique(orig_survey$gameID.x))

## count gender 
count_gender <- orig_survey %>% 
  filter(gender %in% c("M"))
count_gender_ <- count_gender[!duplicated(count_gender$gameID.x),]
table(count_gender_$gender)

## calculate age
calc_age <- orig_survey %>% 
  filter(trial_type %in% c("survey-text"))
calc_age <- calc_age[!duplicated(calc_age$gameID.x),]
calc_age$DOB <- noquote(calc_age$DOB)
calc_age$DOB <- as.numeric(calc_age$DOB)
calc_age <- calc_age[!is.na(calc_age$DOB), ]
calc_age$age <- calc_age$DOT - calc_age$DOB
mean(calc_age$age)
```

## Visualize ALL drawn elements, broken down by toy_id
### (numStrokes)
```{r}
#calculate proportion for all drawn elements
props.toys <- final_data %>% 
  group_by(toy_id, condition, strokeType) %>%
  summarize(N=n()) %>% 
  ungroup() %>% 
  group_by(toy_id, condition) %>% 
  mutate(proportion=N/sum(N))

#plot proportion
props.toys.plot <- props.toys %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType)) +
  geom_bar(stat="identity") +
  facet_grid(.~toy_id) +
  ggtitle("Number of strokes") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) 

ggsave('../results/plots/causaldraw_strokeType_bytoys_proportion.pdf', height = 18, width = 20, units = 'cm', useDingbats = F)
```

## Collapse across toy_ids
```{r}
#calculate proportion for all drawn elements
props <- final_data %>% 
  group_by(condition, strokeType) %>%
  summarise(N=n()) %>%
  mutate(proportion=N/sum(N))

#plot proportion
props.plot <- props %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion) )) +
  geom_bar(stat="identity") +
  ggtitle("Number of strokes") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

ggsave('../results/plots/causaldraw_strokeType_proportion.pdf', height = 18, width =8, units = 'cm', useDingbats = F)
```

#### diff colors, formatting for cogsci
```{r}
#calculate proportion for all drawn elements
props <- final_data %>% 
  group_by(condition, strokeType) %>%
  summarise(N=n()) %>%
  mutate(proportion=N/sum(N))

# make plot
props.plot <- props %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.03f", proportion))) +
  geom_bar(stat="identity") +
  xlab("condition") +
  ylab("proportion") +
  scale_x_discrete(labels=c("depict", "explain")) +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) +  
  theme(text = element_text(size = 4),
        axis.text.x = element_text(size = 6),
        axis.text.y = element_text(size = 9),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "none") +
  # geom_text(size = 3, position = position_stack(vjust = 0.5))
  geom_text(size = 2, position = position_stack(vjust = 0.5))

props.plot + scale_fill_manual(values = c("#7F96AC", "#63948C", "#9FC8B7", "#F4D79F"))

# ggsave('../results/plots/causaldraw_strokeType_proportion.pdf', height = 9, width = 5,  units = 'cm', useDingbats = F)
ggsave('../results/plots/causaldraw_strokeType_proportion.pdf', height = 8, width = 3,  units = 'cm', useDingbats = F)
```


```{r}
#raw count of elements
rawcount.plot <- final_data %>% 
  ggplot(aes(x=condition, fill = strokeType)) +
  geom_bar(position = 'dodge2', stat="count") +
  facet_grid(.~toy_id) +
  # facet_grid(gameID~toy_id) +
  xlab("Condition") +
  ylab("Raw Count") +
  theme_light()

rawcount.plot
```

## Visualize ONLY "entity" elements, i.e., causal and functional
### (numStrokes)
```{r}
#remove non-entity elements
onlyentities <- final_data %>% 
  filter(!(strokeType %in% c("symbol"))) %>% 
  filter(!(strokeType %in% c("background"))) %>% 
  filter(!(strokeType %in% c("light")))
# unique(onlyentities$roi_labelName)

#calculate proportion for entity elements
entity.props.toys <- onlyentities %>% 
  group_by(toy_id, condition, strokeType) %>%
  summarize(N=n()) %>% 
  ungroup() %>% 
  group_by(toy_id, condition) %>% 
  mutate(proportion=N/sum(N))

#plot proportion
entity.props.toys.plot <- entity.props.toys %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType)) +
  geom_bar(stat="identity") +
  facet_grid(.~toy_id) +
  xlab("condition") +
  ylab("proportion") +
  theme_light()

entity.props.toys.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_strokeType_entitytoys_proportion.pdf', height = 18, width = 20,  units = 'cm', useDingbats = F)
```

## collape across toy_id
```{r}
#plot proportion
entity.props <- onlyentities %>% 
  group_by(condition, strokeType) %>%
  summarize(N=n()) %>% 
  ungroup() %>% 
  group_by(condition) %>% 
  mutate(proportion=N/sum(N))

entity.props.plot <- entity.props %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion))) +
  geom_bar(stat="identity") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

entity.props.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_strokeType_entity_proportion.pdf', height = 18, width = 8,  units = 'cm', useDingbats = F)
```

## simple chi-squared test for independence btw condition & causal relevance (pooling all strokes)
```{r}
## convert to counts dataframe 
entityCounts <- entity.props %>%
  mutate(causal=ifelse(strokeType == 'causal', TRUE, FALSE)) %>%
  select(condition,causal,N)
## convert counts to 2x2 contingency table
entityTable <- xtabs(N ~ condition+causal, data=entityCounts)  
## conduct chi-squared test
chisq.test(entityTable)
```

```{r}
#raw count of causal and functional elements
plot.prop2 <- onlyentities %>% 
  ggplot(aes(x=condition, fill = strokeType)) +
  geom_bar(position = 'dodge2', stat="count") +
  facet_grid (.~toy_id) +
  theme_light()

plot.prop2 + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

## Visualize ONLY symbols
### (numStrokes)
``` {r}
#count number of symbol strokes by condition
onlysymbols <- final_data %>% 
  filter(!(strokeType %in% c("causal"))) %>% 
  filter(!(strokeType %in% c("background"))) %>% 
  filter(!(strokeType %in% c("functional")))

#raw count
symbol.plot <- onlysymbols %>% 
  ggplot(aes(x=condition, fill=condition)) +
  geom_bar(position = 'dodge2', stat="count") +
  facet_grid(.~toy_id) +
  xlab("condition") +
  ylab("count") +
  theme_light()

symbol.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

## Visualize ONLY symbols and background
### (numStrokes)
``` {r}
#count number of symbol strokes by condition
nonentities <- final_data %>% 
  filter(!(strokeType %in% c("causal"))) %>% 
  filter(!(strokeType %in% c("functional")))

#raw count
nonentity.plot <- nonentities %>% 
  ggplot(aes(x=condition, fill=condition)) +
  geom_bar(position = 'dodge2', stat="count") +
  facet_grid(.~toy_id) +
  xlab("condition") +
  ylab("count") +
  theme_light()

nonentity.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

```{r}
#plot proportion
nonentity.props <- nonentities %>% 
  group_by(condition, strokeType) %>%
  summarize(N=n()) %>% 
  ungroup() %>% 
  group_by(condition) %>% 
  mutate(proportion=N/sum(N))

nonentity.props.plot <- nonentity.props %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion))) +
  geom_bar(stat="identity") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

nonentity.props.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

```{r}
#calculate proportion of RT for all drawn elements
causaldraw_orig_strokeData <- read_csv('../results/csv/reference/causaldraw_stroke_data_run1.csv')
causaldraw_orig_strokeData <- as.data.frame(causaldraw_orig_strokeData)

#match colnames causaldraw_orig_strokeData and finaldata
#make sketchID
causaldraw_orig_strokeData$toy_id <- paste0(causaldraw_orig_strokeData$toy_type, "_", causaldraw_orig_strokeData$toy_variant)
causaldraw_orig_strokeData$sketchID <- paste0(causaldraw_orig_strokeData$toy_id, ".", causaldraw_orig_strokeData$gameID)

#make strokeIndex
causaldraw_orig_strokeData$strokeIndex <- causaldraw_orig_strokeData$currStrokeNum - 1

processed_orig_strokeData <- causaldraw_orig_strokeData %>% 
  select(c(gameID, endStrokeTime, startStrokeTime, sketchID, strokeIndex))

processed_orig_strokeData$orig_gameID <- processed_orig_strokeData$gameID
processed_orig_strokeData <- processed_orig_strokeData %>% 
  select(-c(gameID))

# merge dataframes
merged_final_data <- merge(final_data, processed_orig_strokeData, by=c("sketchID", "strokeIndex")) 

#cleanup
merged_final_data$orig_gameID <- merged_final_data$orig_gameID.x
merged_final_data <- merged_final_data %>% 
  select(-c(orig_gameID.y))

#calculate RT of original strokes
merged_final_data$totalStrokeTime <- merged_final_data$endStrokeTime - merged_final_data$startStrokeTime

mm <- merged_final_data %>% 
  select(c(orig_gameID, totalStrokeTime, strokeType, condition, toy_id, sketchID, strokeIndex)) 

mm_onlyentities <- mm %>% 
  filter(!(strokeType %in% c("symbols"))) %>% 
  filter(!(strokeType %in% c("background"))) %>% 
  filter(!(strokeType %in% c("light")))

props_rt <- mm %>% 
  group_by(condition, strokeType) %>%
  summarise(totalsum = sum(totalStrokeTime)) %>%
  mutate(proportion = totalsum/sum(totalsum))

#plot proportion
props.plot_RT <- props_rt %>% 
  ggplot(aes(x=condition, y=proportion, fill = strokeType, label=sprintf("%.02f", proportion) )) +
  geom_bar(stat="identity") +
  ggtitle("drawing time") +
  xlab("condition") +
  ylab("proportion") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) +
  geom_text(size = 3, position = position_stack(vjust = 0.5))

props.plot_RT + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))

ggsave('../results/plots/causaldraw_strokeType_drawingTime_proportion.pdf', height = 18, width = 8,  units = 'cm', useDingbats = F)
```

```{r}
props_rtMean <- mm %>% 
  group_by(condition, strokeType) %>%
  summarise(mean = mean(totalStrokeTime)) 

#plot proportion
props.plot_rtMean <- props_rtMean %>% 
  ggplot(aes(x=condition, y=mean, fill = strokeType)) +
  geom_bar(position = 'dodge2', stat="identity") +
  ggtitle("drawing time") +
  xlab("condition") +
  ylab("raw") +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5)) 

props.plot_rtMean + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

```{r}
#raw count of elements
rawcountRT.plot <- mm %>% 
  ggplot(aes(x=condition, fill = strokeType)) +
  geom_bar(position = 'dodge2', stat="count") +
  # facet_grid(.~toy_id) +
  ggtitle("drawing time (raw)") +
  xlab("Condition") +
  ylab("ms") +
  theme_light()

rawcountRT.plot + scale_fill_manual(values=wes_palette(n=4, name="Royal1"))
```

## simple chi-squared test for independence btw condition & causal relevance (pooling all strokes)
```{r}
## convert to counts dataframe 
entityCounts <- entity.props %>%
  mutate(causal=ifelse(strokeType == 'causal', TRUE, FALSE)) %>%
  select(condition,causal,N)
## convert counts to 2x2 contingency table
entityTable <- xtabs(N ~ condition+causal, data=entityCounts)  
## conduct chi-squared test
chisq.test(entityTable)
```

## stats models
```{r}
onlyentities$causal <- ifelse(onlyentities$strokeType == 'causal', TRUE, FALSE) 
final_data$causal <- ifelse(final_data$strokeType == 'causal', TRUE, FALSE) 

# 1. Do people selectively attend to more causally relevant information in the explanation condition, 
# and therefore, draw a higher proportion of causal elements? 
m_entities <- glmer(causal ~ condition + (1|orig_gameID) + (1|sketchID), family="binomial", data = onlyentities)
summary(m_entities)
```

```{r}
# 2. Do people use more symbols in the explanation condition?
sym <- final_data %>% 
  group_by(orig_gameID, sketchID, condition, toy_type, strokeType) %>% 
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(orig_gameID, sketchID, condition, toy_type, strokeType) %>%
  summarise(sum = sum(count)) %>% 
  filter(strokeType == "symbol")

sym_exp <- sym %>% 
  filter(condition %in% c('explanatory'))
mean(sym_exp$sum)

sym_dep <- sym %>% 
  filter(condition %in% c('depictive'))
mean(sym_dep$sum)

m4 <- lmer(sum ~ condition + (1|orig_gameID) + (1|toy_type), data = sym)
summary(m4)
```

```{r}
# 3. Do people use more background details in the depictive condition?
background <- final_data %>% 
  group_by(orig_gameID, sketchID, condition, toy_type, causal, strokeType) %>% 
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(orig_gameID, sketchID, condition, toy_type, causal, strokeType) %>%
  summarise(sum = sum(count)) %>% 
  filter(strokeType == "background")

m5 <- lmer(sum ~ condition + (1 + condition | orig_gameID) + (1 | toy_type), data = background)
summary(m5)
```